\textbf{Are regime changes always bad economics? Evidence from daily financial data}

### 2018-12-29 doc/paper.tex
Added Philippines example to resignations

These results are consistent with the idea that the expected impact of a political event on economic policy is highly important to the directionality of returns. The positive event day abnormal return following resignations is not surprising since resignations typically occur because of poor performance and/or loss of authority. Leaders were often ousted following corruption charges, financial crises, and/or political violence.

For example, consider Muhammad Suharto's resignation from office as the President of Indonesia on May 1998, just after the 1997 Asian Financial Crisis. Prior to the crisis, the Indonesian economy suffered from a number of ailments including crony capitalism, poor corporate governance, growing short-term debt and a corrupt banking system \citep{radelet2000onset}. In addition, Suharto's ill health created considerable policy uncertainty, which only added to the financial panic in Indonesia. Indonesia was also hesitant to adopt structural reforms which further weakened its economic image. As a result, the crisis gave additional ammunition to opposition leaders, and public opposition culminated in riots in mid-May 1998. Suharto eventually lost his military support and was forced to resign.

>>>>

These results are consistent with the idea that the expected impact of a political event on economic policy is highly important to the directionality of returns. The positive event day abnormal return following resignations is not surprising since resignations typically occur because of poor performance and/or loss of authority. Leaders were often ousted following corruption charges, allegations of fraud, financial crises, and/or political violence.

For example, consider Ferdinand Marcos' resignation from office as President of the Philippines in February 1986. Prior to his resignation, the Philippine regime was known for rampant corruption, crony capitalism, extreme inequality, high unemployment, failed import substitution industrialization policy, and oligarchic control of the economy \citep{overholt1986rise, traywick2014}. In fact, the Philippines was the least preferred site for foreign investment amongst East Asian capitalist economies and possessed one of the worst capital investment to economic output ratios in Asia \citep{overholt1986rise}. Marcos held a snap presidential election on February 7, 1986, in which he declared victory despite overwhelming evidence of electoral fraud. Public protests ensued, and two weeks later the military withdrew its support of the Marcos regime \citep{lee2009armed}. Marcos was replaced by his electoral opponent, Corazon Aquino, who had run on a platform of economic liberalization and elimination of crony capitalism \citep{villegas1987philippines}.
